---
title: "HW3"
author: "han"
date: "2/19/2021"
output:
  html_document:
    theme: paper
  github_document: default
---

<!-- BMW: In your YAML header, indent subsections by 2 spaces, not 4.
          Sub-options, like the theme for html_document, need to be indented under the parent option. When you have a sub-option like theme, don't include "default" for the parent option. 
          See what I edited above.
-->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyr)
library(tibble)
library(ggplot2)
library(tidyverse)
library(gridExtra)
library(reshape2) # BMW: Don't use reshape2 and tidyverse packages (eg, dplyr or tidyr) together in the same script. reshape2 isn't supported anymore, and I suggest moving to using tidyr::pivot_longer() and tidyr::pivot_wider() like we practiced in class instead.
library(ggdist)
theme_set(theme_classic())
dictionary <- readr::read_csv("green_dictionary.csv")
green_data <- readr::read_csv("green_data.csv")
```

# Homework 03

<!-- BMW: In general, don't use headings with long blocks of text. It is hard to read. Use regular text instead. -->

You will analyze data looking at the relationship between **green reputation** and three personality traits--**compassion**, **intellectual curiosity**, and **openness to experiences**.
The dataset includes data from **students** and **non-students**.


## For your assignment, do the following.

### Q1: Inspect the item responses (e.g., with graphs or by summarizing distinct values). 

     
```{r Q1}

# Is anything unusual?

Q1set <- filter(green_data, id == 5549) #Searches id for value "5549" 
Q1set.1 <- as.data.frame(t(as.matrix(Q1set) #Flips columns and rows
                           )
                         )
Q1set.1

#Quick summary check
green_data.melt <- melt(green_data, measures.var = across(c:green1:open10)) #Reformat dataset, sets all columns into 1 column to separate as factors

# BMW: I strongly recommend not using melt. It isn't maintained anymore. pivot_longer() and pivot_wider() are the replacements for melt/cast

# BMW: As a stylistic note, avoid using . in object names. '.' sometimes has special meaning in R, and it's best to avoid and using camelCase or snake_case format names instead.

ggplot(green_data.melt) +
  aes(y = value,
      x = id
      ) +
  geom_point()

summary(green_data.melt)


#Dataset has several issues.
#1. Duplicate participant data
#2. Certain data values are off (e.g., -99)

```

### Q2: Compute total scores for the four scales. 

     
```{r Q2}

# Recode variables as needed.

#RECODING
temp_recode <- dictionary %>% #Temporary array of names to be used later
    pull(Item) #Array of names are pulled from the list of values under the "item" column

reverse_recode <- dictionary %>% #Separate temporary array of names to be used later
  filter(Keying == -1 | Keying == -2) %>% #Filters the list by the reverse codes (based off dictionary)
  pull(Item) 

#Dataset for Q2, recodes original dataset "green_data"
Q2set <- green_data %>% 
  mutate( 
    across(all_of(temp_recode), #Recodes across all the columns that match the temp_recode list
           # BMW: Since this is just all the items, you could do `across(everything(), ...)` instead
           ~ na_if(.x, 
                   -99
                   ) #All values that are -99 are recoded into NA
           )
    ) %>% 
  mutate(
    id2 = ifelse(duplicated(id), #Creates new id list and discriminates repeated ID numbers
                 paste0(id,
                        "r"
                        ), #renames duplicate ids  as "id"r
                 id
                 )
    ) %>% 
  mutate(
    across(all_of(reverse_recode),
           ~ recode(.x, 
                    "5" = 1, 
                    "4" = 2, 
                    "3" = 3, 
                    "2" = 4, 
                    "1" = 5
                    )
           )
    ) #Reverse codes based off the dictionary (reverse_recode)

#Rechecking quick summary glance
Q2.melt <- melt(Q2set, 
                measures.var = across(c:green1:open10)
                ) # BMW: Again use pivot_longer()

ggplot(Q2.melt) +
  aes(y = value,
      x = id
      ) +
  geom_point()

summary(Q2.melt) 

#Print out summary statistics
#"Total" scores
Q2set %>% # BMW: You didn't assign this result to an object. Also, these aren't summary statistics. This is the whole dataset. Don't print out a full dataset in your report. 
  rowwise() %>% #By row
  group_by(id2) %>% #By id
  mutate(
    Total_green = sum(c_across(green1:green5), #Summary - sum of all green (20), comp, intel, and open (50)
                      na.rm = TRUE),
    Total_comp = sum(c_across(comp1:comp10),
                     na.rm = TRUE),
    Total_intel = sum(c_across(intel1:intel10),
                      na.rm = TRUE),
    Total_open = sum(c_across(open1:open10),
                     na.rm = TRUE)
  ) %>%
  select(id2,
         Total_green,
         Total_comp,
         Total_intel,
         Total_open)

# BMW: In general, always compute "total" scores for measures as the mean, not the sum. If someone has missing data for an item, that won't affect the mean but will the sum.

#"Mean" Scores
Q2set %>% # BMW: You didn't assign this result to an object. Also, these aren't summary statistics. This is the whole dataset. Don't print out a full dataset in your report. 
  rowwise() %>% #By row
  group_by(id2) %>% #By id
  mutate(
    Total_green = mean(c_across(green1 : green5), 
                      na.rm = TRUE
                      ), 
    Total_comp = mean(c_across(comp1 : comp10), 
                     na.rm = TRUE
                     ),
    Total_intel = mean(c_across(intel1 : intel10), 
                      na.rm = TRUE
                      ),
    Total_open = mean(c_across(open1 : open10), 
                     na.rm = TRUE
                     )
    ) %>% 
  select(id2,
         Total_green,
         Total_comp,
         Total_intel,
         Total_open
         )

```
     
### Q3: Rescale the variables so that they go from 0-100 instead of the original range.


```{r Q3}     

# Name the recaled variables `*_pomp`.
#Dataset for Q3
Q3set <- Q2set %>% 
  mutate(
    across(all_of(temp_recode),
           ~ recode(.x, 
                    "1" = 0,
                    "2" = 25,
                    "3" = 50,
                    "4" = 75,
                    "5" = 100
                   ), 
                   .names = "{.col}_pomp"
           )  
    ) %>% 
  rowwise() %>% # BMW: You can't use rowwise() and group_by() together. rowwise() _is_ group_by(), with the groups being each row. 
  mutate(
    Total_green = mean(c_across(green1_pomp : green5_pomp), 
                      na.rm = TRUE
                      ),
    Total_comp = mean(c_across(comp1_pomp : comp10_pomp), 
                     na.rm = TRUE
                     ),
    Total_intel = mean(c_across(intel1_pomp : intel10_pomp), 
                      na.rm = TRUE
                      ),
    Total_open = mean(c_across(open1_pomp : open10_pomp), 
                     na.rm = TRUE
                     )
    ) %>% 
  mutate(
    student = recode(student, 
                     "1" = "Not a student", 
                     "2" = "Student",
                     .default = "No Response",
                     .missing = "No Response")
    )
#Create summary table for question (Same as Q2set.1 but with 100 as total)
Q3set.1 <- Q3set %>% 
  select(id2,
         Total_green,
         Total_comp,
         Total_intel,
         Total_open
         )

Q3set.1

```     

### Q4: Make plots that illustrate the distributions of the 4 POMP-scored variables.

```{r Q4 fig2, fig.height = 10, fig.width = 15, fig.align = "center"}     

#Reformats dataset to have all the categories as a factor for easier graph (same as before)
Q4set <- melt(Q3set.1, 
              value.name = "POMP_scores", 
              variable.name = "POMP_variables"
              ) # BMW: Again, use pivot_longer() not melt

summary(Q4set)

#Creates plot based off Q4set
Q4set.1 = Q4set %>% 
  filter(POMP_scores != 0) #Removes NA or incorrect data (values = 0)
# BMW: No, this isn't correct. 0 is a valid minimum score. You want na.omit() or drop_na().

Full_hist <- ggplot(Q4set.1) + 
  aes(x = POMP_scores,
      group = POMP_variables,
      color = POMP_variables,
      fill = POMP_variables,
      ) + 
  geom_histogram(alpha = .5, 
                 color = "black", 
                 position = "identity"
                 ) +
  scale_x_continuous("POMP Scores")

Sep_hist <- ggplot(Q4set.1) + 
  aes(x = POMP_scores,
      group = POMP_variables,
      color = POMP_variables,
      fill = POMP_variables,
      ) + 
  geom_histogram(color = "black") +
    facet_grid(~ POMP_variables) + #Split by POMP_variables
  scale_x_continuous("POMP Scores")

grid.arrange(Full_hist, # BMW: You probably don't need both of these plots. The faceted one is clearer.
             Sep_hist)#Merges all the graphs into 1 image

#This graph shows that the green scores are normally distributed while the rest are slightly skewed left.
#Participant scores for all four scales are above half. 
#One possiblity is that these scales are positively correlated to one another. 
#At first glance, this graph shows that, there are more high total score values for comp than rest. 
#Additionally, the graph shows that there are more low total score values for green than the rest.

```  

### Q5: Make scatterplots showing the relationships between **green reputation** and each personality trait.

```{r Q5 fig2, fig.height = 10, fig.width = 15, fig.align = "center"}     

# Include trend lines for **students** and **non-students**.
# What do these plots show?

#Dataset for Q5
Q5set <- Q3set %>% 
  filter(student!="No Response") %>% 
  select(id2,
         Total_green,
         Total_comp,
         Total_intel,
         Total_open,
         student
         )

#3 scatterplots with data separated by student and not a student


GreenXcomp <- ggplot(Q5set) +
  aes(x = Total_green,
      y = Total_comp, 
      color = student
      ) +
  scale_color_manual(values = c("red", 
                                "blue"
                                )
                     ) +
  geom_point() +
  geom_smooth(method = "lm")

GreenXintel <- ggplot(Q5set) +
  aes(x = Total_green,
      y = Total_intel, 
      color = student
      ) +
  scale_color_manual(values = c("red", 
                                "blue"
                                )
                     ) +
  geom_point() +
  geom_smooth(method = "lm")

GreenXopen <- ggplot(Q5set) +
  aes(x = Total_green,
      y = Total_open, 
      color = student
      ) +
  scale_color_manual(values = c("red", 
                                "blue"
                                )
                     ) +
  geom_point() +
  geom_smooth(method = "lm") 

grid.arrange(GreenXcomp,
             GreenXintel,
             GreenXopen,
             nrow=1
             ) # BMW: We will look at it this week, but check out the patchwork package for an elegant way to do this.

```  

<!-- BMW: Put your narrative discussion as regular markdown text, not code comments. -->

Based on the graphs, there seem to be a potential positive correlation between the green reputation survey and each of the other personality trait surveys. 
Additionally the graphs show interactions between the green survey and both intel personality trait survey and open personality trait survey. 

### Q6: Compare **green reputation** for students and non-students using a **rainfall plot** (bar + density + data points).

  
```{r Q6}

ggplot(Q5set) +
  aes(y = student,
      x = Total_green,
      fill = student,
      color = student
      ) +
  geom_jitter(height =.15) +
  geom_boxplot(color = "black",
               alpha = .5,
               width = .3,
               size = .8
               ) +
  ggdist::stat_slab(height = .4,
                    color = "black",
                    size = .2,
                    alpha = .5,
                    position = position_nudge(y = .2)
                    )
```

Overall, the plot does not seem to indicate a notable difference between students and non-students for the green reputation scale. 
However, the plot seems to show that students seem to have larger variance and a lower mean.

### Q7: Compute a summary table of means, SDs, medians, minima, and maxima for the four total scores for students and non-students.

```{r Q7}

Q7set <- Q5set %>%
  group_by(student) %>% 
  summarize(across(c(Total_green:Total_open),
                    list(Mu = ~ mean(.x,
                                      na.rm = TRUE
                                     ),
                         Sigma = ~ sd(.x,
                                      na.rm = TRUE
                                     ),
                         Median = ~ median(.x,
                                           na.rm = TRUE
                                           ),
                         Max = ~ max(.x, 
                                     na.rm = TRUE
                                     ),
                         Min = ~ min(.x, 
                                     na.rm = TRUE
                                     )
                         )
                   )
            ) 
Q7set.1 <- as.data.frame(t(as.matrix(Q7set)
                           )
                         )
Q7set.1


```  

Judging only by the summary statistics, there does not seem to be a difference between students and non-students for any of the personality trait scores (with the possible exception for the mean total score value for comp) or the green reputation scores. 
Nearly all the means between the two groups are the same and around 65 for the scores, 
with the exception of comp (above 70) and green (below 60)
  
  
<!-- BMW: You can delete instruction text like this from your final script. -->

In your assignment, prepare an RMarkdown file that includes both the coding and (for 4-7) narrative descriptions of your results.

