---
title: "HW3"
author: "han"
date: "2/19/2021"
output:
    html_document: default
    github_document: default
    theme: paper
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyr)
library(tibble)
library(ggplot2)
library(tidyverse)
library(gridExtra)
dictionary <- readr::read_csv("green_dictionary.csv")
green_data <- readr::read_csv("green_data.csv")
```

# Homework 03

#### You will analyze data looking at the relationship between **green reputation** and three personality traits--**compassion**, **intellectual curiosity**, and **openness to experiences**.
The dataset includes data from **students** and **non-students**.


## For your assignment, do the following.

### Q1: Inspect the item responses (e.g., with graphs or by summarizing distinct values). 

     
```{r Q1}

# Is anything unusual?

green_data %>% #Summarizes data for each column by max value and min value.
  summarize(
    across(
      c(green1:student),
      list(Max = ~ max(.x, 
                       na.rm = TRUE),
           Min = ~ min(.x, 
                       na.rm = TRUE)
           )
      )
    )

filter(green_data, id == 5549) #Searches id for value "5549" 

#Dataset has several issues.
#1. Duplicate participant data
#2. Certain data values are off (e.g., -99)

```

### Q2: Compute total scores for the four scales. 

     
```{r Q2}

# Recode variables as needed.

temp_recode <- dictionary %>% #Temporary array of names to be used later
  pull(Item) #Array of names are pulled from the list of values under the "item" column

Q2set <- green_data %>% #Dataset for Q2, recodes original dataset "green_data"
  mutate( #Recodes across all the columns that match the temp_recode list
    across(
      all_of(temp_recode), 
           ~ na_if(.x, 
                   -99)
      )
    ) %>% #All values that are -99 are recoded into NA
  mutate( #Creates new id list and discriminates repeated ID numbers
    id2 = ifelse(
      duplicated(id),
      paste0(id, 
             "r"), 
      id)
    ) 

Q2set %>% #Rechecking quick summary glance
  summarize(
    across(
      c(green1 : student),
      list(Max = ~ max(.x, 
                       na.rm = TRUE),
           Min = ~ min(.x, 
                       na.rm = TRUE)
           )
      )
    )

reverse_recode <- dictionary %>% #Separate temporary array of names to be used later
  filter(Keying == -1 | Keying ==-2) %>% #Filters the list by the reverse codes (based off dictionary)
  pull(Item)    

Q2set.1 <- Q2set%>% #New dataset with reverse coding 
  mutate(
    across(
      all_of(reverse_recode),
           ~ recode(.x, 
                    "5" = 1, 
                    "4" = 2, 
                    "3" = 3, 
                    "2" = 4, 
                    "1" = 5)
      )
    ) #Reverse codes based off the dictionary (reverse_recode)

Q2set.1 %>% #Print out summary statistics
  rowwise() %>% #By row
  group_by(id2) %>% #By id
  mutate(
    Total_green = sum(c_across(green1 : green5), #Summary - sum of all green (20), comp, intel, and open (50)
                      na.rm = TRUE), 
    Total_comp = sum(c_across(comp1 : comp10), 
                     na.rm = TRUE),
    Total_intel = sum(c_across(intel1 : intel10), 
                      na.rm = TRUE),
    Total_open = sum(c_across(open1 : open10), 
                     na.rm = TRUE)
    ) %>% 
  select(id2,
         Total_green,
         Total_comp,
         Total_intel,
         Total_open)

```
     
### Q3: Rescale the variables so that they go from 0-100 instead of the original range.


```{r Q3}     

# Name the recaled variables `*_pomp`.

Q3set <- Q2set.1 %>% #Dataset for Q3
  mutate(
    across(c(green1 : green5), #Change for green data
           ~.x * 4, #Multiply green data by 4 (Total equals 100)
           .names = "{.col}_pomp") #creates new columns for ^^ named *column*_pomp 
    ) %>% 
  mutate(
    across(c(comp1 : open10),
           ~.x * 2, #Same as before but multiply rest by 2 (Total equal 100)
           .names = "{.col}_pomp")
    )

Q3set_Final <- Q3set %>% #Create summary table for question (Same as Q2set.1 but with 100 as total)
  rowwise() %>%
  group_by(id2) %>% 
  mutate(Total_green = sum(c_across(green1_pomp : green5_pomp), 
                           na.rm = TRUE),
         Total_comp = sum(c_across(comp1_pomp : comp10_pomp), 
                          na.rm = TRUE),
         Total_intel = sum(c_across(intel1_pomp : intel10_pomp), 
                          na.rm = TRUE),
         Total_open = sum(c_across(open1_pomp : open10_pomp), 
                          na.rm = TRUE)
         ) %>% 
  select(id2,
         Total_green,
         Total_comp,
         Total_intel,
         Total_open,
         student)

Q3set_Final

```     

### Q4: Make plots that illustrate the distributions of the 4 POMP-scored variables.

```{r}     

Q4set <- Q3set_Final %>% #Creates plot based off Q3
  select(id2,
         Total_green, 
         Total_comp, 
         Total_intel, 
         Total_open) %>%
  pivot_longer(., 
               cols = c(Total_green,
                        Total_comp,
                        Total_intel,
                        Total_open), 
               names_to = "POMP_variables", 
               values_to = "POMP_scores") #Reformats dataset to have all the categories as a factor for easier graph

ggplot(Q4set) +
  aes(x = id2, 
      y = POMP_scores) + 
  facet_grid(~ POMP_variables) + #Split by POMP_variables
  geom_point() +
  scale_x_discrete("ID") +
  scale_y_continuous("POMP Scores") +
  theme_bw()

```  

### Q5: Make scatterplots showing the relationships between **green reputation** and each personality trait.

```{r Q5 fig2, fig.height = 10, fig.width = 15, fig.align = "center"}     

# Include trend lines for **students** and **non-students**.
# What do these plots show?

Q5set <- Q3set_Final %>% #Dataset for Q5
  mutate(
    student = recode(student, 
                     "1" = "Not a student", 
                     "2" = "Student", 
                     .default = "No Response", 
                     .missing = "No Response")
    ) #Recode to student and not a student

#These are a set of ggplots showing a scatterplot of student, not a student and no responses
a <- ggplot(Q5set) +
  aes(x = Total_green,
      y = Total_comp, 
      color = student) +
  geom_point() +
  scale_color_manual(values = c("black", 
                                "red", 
                                "blue")
                     ) +
  geom_smooth(method = "lm") +
  theme_classic()

b <- ggplot(Q5set) +
  aes(x = Total_green,
      y = Total_intel, 
      color = student) +
  geom_point() +
  scale_color_manual(values = c("black", 
                                "red", 
                                "blue")
                     ) +
  geom_smooth(method = "lm") +
  theme_classic()

c <- ggplot(Q5set) +
  aes(x = Total_green,
      y = Total_open,  
      color = student) +
  geom_point() +
  scale_color_manual(values = c("black", 
                                "red", 
                                "blue")
                     ) +
  geom_smooth(method = "lm") +
  theme_classic()

#Same dataset as last one but removed all NA and incorrect data
Q5set.1 <- Q3set_Final %>% 
  mutate(
    student = recode(student, 
                     "1" = "Not a student", 
                     "2" = "Student")
    )

#Same plots as last time but without NA and incorrect data
d <- ggplot(data = subset(Q5set.1, 
                          !is.na(student)
                          )
            ) +
  aes(x = Total_green,
      y = Total_comp, 
      color = student) +
  scale_color_manual(values = c("red", 
                              "blue")
                     ) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_classic()

e <- ggplot(data = subset(Q5set.1, 
                          !is.na(student)
                          )
            ) +
  aes(x = Total_green,
      y = Total_intel, 
      color = student) +
  scale_color_manual(values = c("red", 
                              "blue")
                     ) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_classic()

f <- ggplot(data = subset(Q5set.1, 
                          !is.na(student)
                          )
            ) +
  aes(x = Total_green,
      y = Total_open, 
      color = student) +
  scale_color_manual(values = c("red", 
                              "blue")
                     ) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_classic()


grid.arrange(a,
             b,
             c,
             d,
             e,
             f, 
             nrow = 2)#Merges all the graphs into 1 image


```  

### Q6: Compare **green reputation** for students and non-students using a **rainfall plot** (bar + density + data points).

  
```{r Q6}


```  

### Q7: Compute a summary table of means, SDs, medians, minima, and maxima for the four total scores for students and non-students.

```{r Q7}

Q5set %>%
  group_by(student) %>% 
  summarize(across(c(Total_green:Total_open),
                    list(Mu = ~mean(.x,
                                    na.rm = TRUE),
                         Sigma = ~sd(.x,
                                     na.rm=TRUE),
                         Median = ~median(.x,
                                          na.rm=TRUE),
                         Max=~max(.x, 
                                  na.rm = TRUE),
                         Min=~min(.x, 
                                  na.rm = TRUE)
                         )
                   )
            )

```  
  
In your assignment, prepare an RMarkdown file that includes both the coding and (for 4-7) narrative descriptions of your results.

