---
title: "Beer Advocate: ABV and quality ratings"
author: "Your Name Here"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(here)
library(dplyr)
library(tidyr)
library(tibble)
library(ggplot2)
library(tidyverse)
library(gridExtra)
library(reshape2)
library(ggdist)
```

For this activity, download the data file at this location to the `data` subfolder in your `participation` folder. 
This dataset contains information about different catagories of beer as rated on <beeradvocate.com>.
The data are originally from [here](http://scottjanish.com/relationship-of-abv-to-beer-scores/).

```{r}
dir.create(here::here("3_4_21"), recursive = TRUE)
dat <- read_csv("https://raw.githubusercontent.com/USF-Psych-DataSci/Classroom/master/data/beer-advocate.csv",
                col_types = cols(
                  `Beer Category` = col_character(),
                  `Average ABV` = col_double(),
                  rAVG = col_double()
                  )
)

graph = ggplot(dat) +
  aes(x=`Average ABV`, y=rAVG) +
  geom_jitter()

ggsave(here::here("3_4_21", "plotforworksheet_3_4_21.pdf"), graph)

summarytable = dat %>% 
  summarize(across(c(`Average ABV`: rAVG),
                     list(Mu = ~ mean(.x,
                                      na.rm = TRUE
                                     ),
                         Sigma = ~ sd(.x,
                                      na.rm = TRUE
                                     )
                         )
                  ),
            r = cor(`Average ABV`, rAVG, use = "pairwise")
            )
write_csv(dat,
          here::here("3_4_21", "newtable_3_4_21.csv")
          )
write_csv(summarytable,
          here::here("3_4_21", "summarytable_3_4_21.csv")
          )
```

The dataset contains 3 variables:

  1. Beer category
  2. Average alcohol by volume (ABV) in percentage (%)
  3. Average quality rating (rAVG) on a 1–5 scale
  
You should write a script to do the following:

  1. Download the dataset with an appropriate filename.
  2. Import the dataset into R.
     Be sure to check for any importing problems and correct as needed.
  3. Make a figure illustrating the relationship between ABV and beer quality.
  4. Compute a summary table with the mean and SD of each variable, along with their correlation.
  5. Describe the results.
